\textit{Supporting Information for}: Memory for television episodes preserves event content while introducing new across-event similarities

### 2020-01-07 paper/supporting_information.tex
WIP embedding optimization section

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage[font=small,labelfont=bf]{caption}
\usepackage{geometry}
\usepackage{natbib}
\usepackage{pxfonts}
\usepackage{graphicx}
\usepackage{newfloat}
\usepackage{setspace}
%\doublespacing

@@

\begin{figure}[p!]
\centering
\includegraphics[width=0.75\textwidth]{figs/topic_words}
\caption{\small \textbf{Topics discovered in \textit{Sherlock}.} We applied a topic model to hand-annotated information about 1000 scenes spanning the 45 minute episode.  We identified 27 unique topics with non-zero weights (we used $K=100$ topics to fit the model).  Each topic comprises a distribution of weights over all words in the vocabulary.  For each topic, we show the words with the 10 largest weights, along with a suggested description of the topic.}
\label{fig:topics}
\end{figure}

@@

\begin{figure}[p!]
\centering
\includegraphics[width=1\textwidth]{figs/feature_value}
\caption{\small \textbf{Feature importance analysis.} \textbf{A.} Contributions of each feature type to the structure of the video trajectory. The bar heights reflect the correlation between the video trajectory computed using all features with a video trajectory computed using all features except the indicated feature.  (Lower bars reflect features that contribute more substantially to the video trajectory's shape.) \textbf{B.} Which features are preserved during recall?  The bar heights reflect the (average) across-participant correlations between the video and recall trajectories.  Error bars denote bootstrap-estimated standard error of the mean.  \textbf{C.} Feature correlation matrix.  Each entry displays the correlation between video topic trajectories created using only the indicated (row/column) features.}
\label{fig:feature-importance}
\end{figure}

@@

Next, we wondered how the different types of features might relate.  For example, knowing which character is in focus during a given scene may also provide information about which character is speaking.  We computed video topic trajectories for each feature in turn, and then compared the upper triangles of the temporal correlation matrices of all pairs of features.  This provided additional confirmation that the shape of the full trajectory (including all types of features) was largely driven by narrative details.  We also found that character-driven features (characters on screen, characters speaking, and characters in focus) were strongly correlated.  Other details, such as the presence or absence of music, led to very different topic trajectories (Fig.~\ref{fig:feature-importance}C).

>>>>

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage[font=small,labelfont=bf]{caption}
\usepackage{geometry}
\usepackage{natbib}
\usepackage{pxfonts}
\usepackage{graphicx}
\usepackage{newfloat}
\usepackage{setspace}
\usepackage{placeins}
%\doublespacing

@@

\begin{figure}[p!]
\centering
\includegraphics[width=0.65\textwidth]{figs/topic_words}
\caption{\small \textbf{Topics discovered in \textit{Sherlock}.} We applied a topic model to hand-annotated information about 1000 scenes spanning the 45 minute episode.  We identified 27 unique topics with non-zero weights (we used $K=100$ topics to fit the model).  Each topic comprises a distribution of weights over all words in the vocabulary.  For each topic, we show the words with the 10 largest weights, along with a suggested description of the topic.}
\label{fig:topics}
\end{figure}
\FloatBarrier

@@

\begin{figure}[t]
\centering
\includegraphics[width=1\textwidth]{figs/feature_value}
\caption{\small \textbf{Feature importance analysis.} \textbf{A.} Contributions of each feature type to the structure of the video trajectory. The bar heights reflect the correlation between the video trajectory computed using all features with a video trajectory computed using all features except the indicated feature.  (Lower bars reflect features that contribute more substantially to the video trajectory's shape.) \textbf{B.} Which features are preserved during recall?  The bar heights reflect the (average) across-participant correlations between the video and recall trajectories.  Error bars denote bootstrap-estimated standard error of the mean.  \textbf{C.} Feature correlation matrix.  Each entry displays the correlation between video topic trajectories created using only the indicated (row/column) features.}
\label{fig:feature-importance}
\end{figure}

@@

Next, we wondered how the different types of features might relate.  For example, knowing which character is in focus during a given scene may also provide information about which character is speaking.  We computed video topic trajectories for each feature in turn, and then compared the upper triangles of the temporal correlation matrices of all pairs of features.  This provided additional confirmation that the shape of the full trajectory (including all types of features) was largely driven by narrative details.  We also found that character-driven features (characters on screen, characters speaking, and characters in focus) were strongly correlated.  Other details, such as the presence or absence of music, led to very different topic trajectories (Fig.~\ref{fig:feature-importance}C).
\FloatBarrier

\subsection*{Creating a low-dimensional embedding space}
Figures~5 and 6C in the main text display two-dimensional projections of the 100-dimensional topic trajectories for the video (5A, 6C), average recall (5B), and each individual's recall (5C, 6C).  We created these embeddings using the Uniform Manifold Approximation and Projection algorithm \citep[UMAP;][]{McInEtal18} called from our high-dimensional visualization and text analysis software, \texttt{HyperTools}~\citep{HeusEtal18a}.  An advantage of the UMAP algorithm over comparable manifold learning techniques (such as $t$-SNE) is that UMAP explicitly attempts to preserve the global structure of the data \citep{McInEtal18,BechEtal19} by constructing a space where distance on the manifold is standard Euclidean distance, with respect to the global coordinate system.  This was important in our use case, as we wanted to visualize both the evolving structure of the video and the spatial relationships between presented and recalled content.

UMAP achieves a balance between representing local and global structure via a subset of its hyper-parameters: \texttt{n\_neighbors} , \texttt{spread}, and \texttt{min\_dist}.  The \texttt{n\_neighbors} hyper-parameter ($K$) denotes the number of nearest neighbors to consider in constructing the high-dimensional fuzzy simplicial set for each datapoint.  \texttt{Spread} ($\gamma$) and \texttt{min\_dist} ($\delta$) function together to create the differentiable decay curve used to approximate the injective function used to map between high- and low-dimensional fuzzy simplicial sets.  In essence, \texttt{min\_dist} determines the degree to which nearby points are clustered or expanded, relative to to the overall \texttt{spread}.

To optimize the manifold space shown in Figures~5 and 6C, we performed a grid search over pre-specified values of these hyper-parameters, as well as a pre-specified set of random states ($\tau$).  Additionally, as described in \textit{Methods}, we ensured the video and recall events were projected onto the \textit{same} low-dimensional manifold by fitting the embedding model to a stacked matrix of
